%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\documentclass[letterpaper,12pt]{fed-res} % Make sure you have the fed-res.cls file in the same directory
\begin{document}

%-------------------------------------------------------------------------------
%	HEADING INFORMATION
%-------------------------------------------------------------------------------
\begin{center}
    \textbf{\Huge \scshape Diego Alejandro Flores Quintero} \\ \vspace{1pt}
    Armenia, Quindío \ $|$ \
    \href{http://wa.me/+573042902576}{+57 304\,290\,2576} \ $|$ \
    \href{mailto:floresquintero.da@gmail.com}{floresquintero.da@gmail.com} \\[1pt]
    \href{https://www.diegnghtmr.me}{Portfolio: diegnghtmr.me} \ $|$ \
    \href{https://github.com/diegnghtmr}{GitHub: diegnghtmr} \ $|$ \
    \href{https://www.linkedin.com/in/diego-alejandro-flores-quintero/}{LinkedIn: diego-alejandro-flores-quintero}
\end{center}

%-------------------------------------------------------------------------------
%	RESUME CONTENT
%-------------------------------------------------------------------------------

%-----------WORK EXPERIENCE----------- 
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Freelance Digital Developer}{May 2024 -- January 2026}
            {Self-Employed}{Armenia, Quindío}
            \resumeItemListStart
                \resumeItem{Developed modern web applications using React, Next.js, and Spring Boot, integrating SEO best practices to maximize search rankings and digital reach.}
                \resumeItem{Designed and implemented robust backend solutions based on Clean Architecture and Microservices, ensuring system scalability and code maintainability.}
                \resumeItem{Managed the full software development lifecycle (SDLC), delivering high-performance, custom software solutions deployed on cloud infrastructure.}
                \resumeItem{Executed efficient API integrations and database optimizations, maintaining high quality and security standards across all projects.}
            \resumeItemListEnd

        \resumeSubheading
            {Teaching Assistant for Mathematics and Programming}{August 2024 -- November 2025}
            {Universidad del Quindío}{Armenia, Quindío}
            \resumeItemListStart
                \resumeItem{Taught supplemental lessons in Mathematics and Programming, clarifying doubts and reinforcing key concepts.}
                \resumeItem{Developed and solved practical exercises to strengthen the understanding of class topics.}
                \resumeItem{Provided academic support during tutoring sessions, improving student performance and motivation.}
                \resumeItem{Prepared study guides and materials to facilitate midterm and final exam preparation.}
            \resumeItemListEnd

        \resumeSubheading
            {Virtual Assistant}{December 2022 -- April 2024}
            {Professor Mg. Will Yesid López Echeverri}{Armenia, Quindío}
            \resumeItemListStart
                \resumeItem{Coordinated meetings and tasks using Slack and Zoom, ensuring agile and effective communication.}
                \resumeItem{Managed documents and projects through Microsoft Office, Google Workspace, and cloud platforms (OneDrive, Google Drive).}
                \resumeItem{Organized academic events, enhancing planning and time management skills.}
                \resumeItem{Created digital content and websites using Canva and content management tools, boosting online presence.}
                \resumeItem{Implemented Notion for project management and produced educational videos.}
                \resumeItem{Drafted academic documents in APA format and handled confidential information with integrity.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
