\resumeSubHeadingListStart
    \resumeSubheading
        {Freelance Digital Developer}{May 2024 -- January 2026}
        {Self-Employed}{Armenia, Quindío}
        \resumeItemListStart
            \resumeItem{Developed modern web applications using React, Next.js, and Spring Boot, integrating SEO best practices to maximize search rankings and digital reach.}
            \resumeItem{Designed and implemented robust backend solutions based on Clean Architecture and Microservices, ensuring system scalability and code maintainability.}
            \resumeItem{Managed the full software development lifecycle (SDLC), delivering high-performance, custom software solutions deployed on cloud infrastructure.}
            \resumeItem{Executed efficient API integrations and database optimizations, maintaining high quality and security standards across all projects.}
        \resumeItemListEnd

    \resumeSubheading
        {Teaching Assistant for Mathematics and Programming}{August 2024 -- November 2025}
        {Universidad del Quindío}{Armenia, Quindío}
        \resumeItemListStart
            \resumeItem{Taught supplemental lessons in Mathematics and Programming, clarifying doubts and reinforcing key concepts.}
            \resumeItem{Developed and solved practical exercises to strengthen the understanding of class topics.}
            \resumeItem{Provided academic support during tutoring sessions, improving student performance and motivation.}
            \resumeItem{Prepared study guides and materials to facilitate midterm and final exam preparation.}
        \resumeItemListEnd

    \resumeSubheading
        {Virtual Assistant}{December 2022 -- April 2024}
        {Professor Mg. Will Yesid López Echeverri}{Armenia, Quindío}
        \resumeItemListStart
            \resumeItem{Coordinated meetings and tasks using Slack and Zoom, ensuring agile and effective communication.}
            \resumeItem{Managed documents and projects through Microsoft Office, Google Workspace, and cloud platforms (OneDrive, Google Drive).}
            \resumeItem{Organized academic events, enhancing planning and time management skills.}
            \resumeItem{Created digital content and websites using Canva and content management tools, boosting online presence.}
            \resumeItem{Implemented Notion for project management and produced educational videos.}
            \resumeItem{Drafted academic documents in APA format and handled confidential information with integrity.}
        \resumeItemListEnd
\resumeSubHeadingListEnd
